In this dissertation, I developed scaleable data visualization methods enabling scholar's accompaniments at a glance.


Evaluation of scholarly achievements in academia is largely based on the researcher's publication record. This record is communicated in exhaustive detail in the researcher's curriculum vitae (CV) or in summary via her/his {\it h}-index. The {\it h}-index, although a convenient abstraction, considers neither the time of the publication nor the impact factor ($IF$) of the journal where it appeared. In this article I present a novel method that visually complements the {\it h}-index, revealing at a glance the nature of a researcher's scholastic record. This method (aka Scholar Plot and Academic Garden) is particularly appropriate for web interfaces, as it produces information that is compact and simple, yet highly illuminating. The method uses Google Scholar, Impact Factor and NSF/NIH/NASA funding data to create a temporal representation of a researcher's publication/funding record that blends publication prestige with paper popularity and funding information. Scholar Plot aids to obtain an insightful appraisal of academics at one's fingertips.


Academic Garden applies to individual academics, departments, colleges, and any other academic group thereof, such as a research lab or a project team. Academic Garden uses the flower metaphor to visually articulate performance for academic entities. The width of the flower's stem is commensurate to the academic funding this entity received (`juice conduit'). The height of the flower
s stem is commensurate to the impact of the entity's intellectual products (`visibility'). The diameter of the flower's disc is commensurate to the prestige of the venues where these products appeared (`fancy factor'). Scholar Plot and Academic Garden bring clarity, transparency, and fairness in hiring, promotion, tenure, and funding decisions.



